Practical Machine Learning - Prediction Assignment Writeup
==========================================================

author: "Kyaw Thu"
date: "Tuesday, September 22, 2015"
output: html_document

#Introduction#
Jawbone Up,Nike FuelBand, andFitbit are popular devices to measure the personal activities data inexpensively and conveniently.One thing that people regularly do is quantify how much of a particular activity they do, but they rarely quantify how well they do it.

In this project, targeted goal will be to use data from accelerometers on the belt, forearm, arm, and dumbell of 6 participants and predict how they do their exercise. They were asked to perform barbell lifts correctly and incorrectly in 5 different ways. 

##Data Source##
Training and test data are downloaded from the follwing link and located in Data folder:

<https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv> ;

<https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv>


Data need to be analysed about individual activity using caret and randomForest packages.
To It will produce correct answers for each of the 20 test data cases provided in this assignment. 
Seed value will be used for consistent results.

#Required packages for prediction# 
```{r}
library(Hmisc)
library(caret)
library(randomForest)
library(foreach)
library(doParallel)
set.seed(54321)
options(warn=-1)
```


Some values contained a "#DIV/0!" that wii be replaced with an NA value.


#Reading data sets#


 
```{r}
setwd("C:/Users/User/Desktop/Rdirectory/Practical-Machine-Learning")
training_data <- read.csv("pml-training.csv", na.strings=c("#DIV/0!") )
test_data <- read.csv("pml-testing.csv", na.strings=c("#DIV/0!") )
```

#Casting columns to be numeric from Col 8 to the end#

```{r}
for(i in c(8:ncol(training_data)-1)) {training_data[,i] = as.numeric(as.character(training_data[,i]))}

for(i in c(8:ncol(test_data)-1)) {test_data[,i] = as.numeric(as.character(test_data[,i]))}
```

Some columns are in blanks. They do not contribute for prediction work. Complete column data will be named as "c-data" that are useful for processing.
 

#Determining complete columns data#

```{r}
c_data <- colnames(training_data[colSums(is.na(training_data)) == 0])[-(1:7)]
model_data <- training_data[c_data]
c_data
```

We now have the model data built from our feature data set.
We are using 60:40 proportion for train and test data.

#Data Partition#

```{r}
idx <- createDataPartition(y=model_data$classe, p=0.60, list=FALSE )
training <- model_data[idx,]
testing <- model_data[-idx,]
```

 We make use of parallel processing with randomForest to improve processing speed.


```{r}
registerDoParallel()
x <- training[-ncol(training)]
y <- training$classe

rf <- foreach(ntree=rep(150, 6), .combine=randomForest::combine, .packages='randomForest') %dopar% {
randomForest(x, y, ntree=ntree) 
}
```

#Report: Error in training and test data sets#
```{r}
predictions1 <- predict(rf, newdata=training)
confusionMatrix(predictions1,training$classe)


predictions2 <- predict(rf, newdata=testing)
confusionMatrix(predictions2,testing$classe)
```

Conclusions and Test Data Submit
--------------------------------

Confusion matrix announced that this model is very accurate. PCA and other models are not good at accuracy, but this algorithm produce around 99% accurate I expected nearly all of the submitted test cases to be correct.  It turned out they were all correct.

Prepare the submission. (using COURSERA provided code)

```{r}
pml_write_files = function(x){
  n = length(x)
  for(i in 1:n){
    filename = paste0("problem_id_",i,".txt")
    write.table(x[i],file=filename,quote=FALSE,row.names=FALSE,col.names=FALSE)
  }
}


x <- test_data
x <- x[c_data[c_data!='classe']]
answers <- predict(rf, newdata=x)

answers

pml_write_files(answers)
```
