---
title: "Prediction on Exercise Behaviour"
author: "Kyaw Thu"
date: "Tuesday, September 15, 2015"
output: html_document
---


```{r, echo=FALSE}

```



#Introduction#
Jawbone Up,Nike FuelBand, andFitbit are popular devices to measure the personal activities data inexpensively and conveniently.One thing that people regularly do is quantify how much of a particular activity they do, but they rarely quantify how well they do it.

In this project, targeted goal will be to use data from accelerometers on the belt, forearm, arm, and dumbell of 6 participants and predict how they do their exercise. They were asked to perform barbell lifts correctly and incorrectly in 5 different ways. 

##Data##
Training and test data are downloaded from the follwing link and located in Data folder:

<https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv> ;

<https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv>

```{r,echo=FALSE}
#setwd("C:/Users/User/Desktop/Rdirectory/Data")
```
#Read Data#
```{r,echo=FALSE}
training= read.csv(""C:/Users/User/Desktop/Rdirectory/Practical-Machine-Learning/Data/pml-training.csv"", na.strings=c("", "NA", "NULL"))

testing = read.csv("C:/Users/User/Desktop/Rdirectory/Practical-Machine-Learning/Data/pml-testing.csv"), na.strings=c("", "NA", "NULL"))

dim(training)

dim(testing)
```

